Software for Automated Theorem Proving Based on the Calculus of Positively Constructed Formulas\thanks{Ok}

### 2015-09-04 paper.tex
Conclusion has been revised.

\subsection{Memory management.}
Allocation of memory for fixed size records is implemented by means of standard approach, which is similar to \cite{gmemory}. Array of structures is allocated with memory manager of operation system and then converted to freelists. New structures are allocated from the freelists, and released ones are returned back to the freelists. If a list is exhausted a new array is allocated from heap memory if any.

@@

%=======================================================================
%==========================EXPERIMENTS==================================
%=======================================================================
\section{Experiments}
Testing the developed prover was performed on problems form TPTP \cite{tptp} library version 5.4.0 (Thousands of Problems for Theorem Provers, www.tptp.org). This library is the de facto standard for testing the ATP provers. The type of problems that were chosen are the problems of FOF without equality. Total number of problems is 1221 with rating from 0.0 to 1.0. Total number of solved problems is 780. The maximal rating of solved problem is 0.62. The best results among domains presented in the Table~1.

@@

Prover shown good results for problems, whose formalization in the PCF language contains quite large conjuncts.

@@

%=======================================================================
%==========================CONCLUSION===================================
%=======================================================================
\section*{Conclusion}
In this paper, we presented the results of the PCF calculus investigation in the context of the automatic theorem proving. The main result is a prover program implemented based on the PCF calculus. Several logical inference strategies were devised, adopted from other papers and implemented in this prover: memory sharing, lazy concretization, $k,m$--condition, parallel strategies. A special global data structure (Proof state tree) has been developed. Most of the strategies are implemented on the base of the structure.

>>>>

\subsection{Memory management}
Allocation of memory for fixed size records is implemented by means of standard approach, which is similar to \cite{gmemory}. Array of structures is allocated with memory manager of operation system and then converted to freelists. New structures are allocated from the freelists, and released ones are returned back to the freelists. If a list is exhausted a new array is allocated from heap memory if any.

@@

%=======================================================================
%==========================EXPERIMENTS==================================
%=======================================================================
\section{Experiments}
Testing the developed prover is being performed on problems form TPTP \cite{tptp} library version 5.4.0 (Thousands of Problems for Theorem Provers, www.tptp.org). This library is the de facto standard for testing ATP provers. The type of problems that were chosen are the problems of FOF without equality. Total number of problems is 1221 with rating from 0.0 (very easy) to 1.0 (unresolved). Total number of solved problems is 780. The maximal rating of solved problem is 0.62. The best results among domains presented in the Table~1.

@@

Prover shown good results for problems, whose formalization in the PCF language contains large conjuncts (type conditions).

@@

%=======================================================================
%==========================CONCLUSION===================================
%=======================================================================
\section*{Conclusion}
In this paper, we presented the results of the positively constructed formulas (PCF) calculus investigation in the context of the automatic theorem proving. The main result is a prover program implemented based on the PCF calculus. Several logical inference strategies were devised, adopted from other papers and implemented in this prover: memory sharing, lazy concretization, $k,m$--condition, parallel strategies. A special global data structure (proof state tree) has been developed. Most of the strategies are implemented on the base of the structure.
